Defining properties regulating pioneer-factor binding and function

### 2023-01-05 manuscript/manuscript.qmd
update outline of Extended Data figures

| Reagent                               | Source/vendor              | Catalog/accession \# | Notes                   |
|---------------------|-----------------|-----------------|-----------------|
| pMT-puro                              | AddGene                    | 17923                |                         |
| Gibson Cloning                        | New England Biolabs        | E2611                |                         |
| Schneider's Medium                    | Thermo Fisher Scientific   | 21720001             |                         |
| Fetal Bovine Serum                    | Omega Scientific           | FB-02                |                         |
| Antibiotic/antimycotic                | Thermo Fisher Scientific   | 15240062             |                         |
| Effectene Transfection Reagent        | Qiagen                     | 301427               |                         |
| PVDF Membrane                         |                            |                      |                         |
| Formaldehyde                          |                            |                      |                         |
| Protease inhibitor tablets            |                            |                      |                         |
| NEBNext Ultra II DNA library prep kit |                            |                      |                         |
| TruSeq v2 RNA library prep kit        |                            |                      |                         |
| Trizol                                |                            |                      |                         |
| **Antibodies**                        |                            |                      |                         |
| Anti-Zld                              | Harrison et al., 2010      |                      | ChIP: 6 µL , WB: 1:750  |
| Anti-Grh                              | Harrison et al., 2010      |                      | ChIP: 8 µL, WB: 1:1000  |
| Anti-Twi                              | He et al., 2015            |                      | ChIP: 10 µg, WB: 1:1000 |
| Anti-HA-peroxidase clone 3F10         | Roche                      | 12013819001          | WB: 1:500               |
| Anti-Tubulin DM1A                     | Sigma                      | T6199-200UL          | WB: 1:5000              |
| goat anti-rabbit IgG-HRP conjugate    | Bio-Rad                    | 1706515              | WB: 1:3000              |
| Anti-HA clone 12CA5                   | Roche                      |                      | ChIP: 7.5 µL            |
| Anti-H3K27me3                         | Cell Signaling Technology  | C36B11; Lot #19      | WB: 1:1000, CR: 0.5 µL  |
|                                       |                            |                      |                         |
|                                       |                            |                      |                         |

@@

-   RNA-seq data to show expression of S2 and not Kc cell markers.

@@

**Extended Data Figure 2: Ectopically expressed Zld and Grh bind to thousands of sites in S2 cells.**

-   ChIP-seq replicate correlation

-   Genome browser and heatmaps for all ChIP peaks?

-   IgG and WT controls for antibody specificity

**Extended Data Figure 3: Ectopic expression of pioneer factors in S2 cells leads to widespread changes to chromatin accessibility.**

-   ATAC PCA plot

-   ATAC replicate correlation

-   Example genome browsers?

**Extended Data Figure 4: Zld and Grh bind to chromatin rapidly after induction of protein expression**

@@

**Extended Data Figure 5: Zld and Grh binding promotes transcriptional activation at a subset of binding sites**

@@

-   RNA-seq replicate correlation

@@

**Extended Data Figure 6: Twist binding leads to chromatin opening and transcriptional activation**

-   Twi ATAC PCA, volcano, and examples

-   TWI RNA-seq PCA, volcano, and examples

@@

**Extended Data Figure 7: Chromatin features associated with Zld, Grh and Twi binding sites**

@@

**Extended Data Figure 8: Zld, Grh and Twi do not bind preferentially to motifs in a particular position on nucleosomes**

>>>>

| Reagent                               | Source/vendor             | Catalog/accession \# | Notes                   |
|--------------------|------------------|------------------|------------------|
| pMT-puro                              | AddGene                   | 17923                |                         |
| Gibson Cloning                        | New England Biolabs       | E2611                |                         |
| Schneider's Medium                    | Thermo Fisher Scientific  | 21720001             |                         |
| Fetal Bovine Serum                    | Omega Scientific          | FB-02                |                         |
| Antibiotic/antimycotic                | Thermo Fisher Scientific  | 15240062             |                         |
| Effectene Transfection Reagent        | Qiagen                    | 301427               |                         |
| PVDF Membrane                         |                           |                      |                         |
| Formaldehyde                          |                           |                      |                         |
| Protease inhibitor tablets            |                           |                      |                         |
| NEBNext Ultra II DNA library prep kit |                           |                      |                         |
| TruSeq v2 RNA library prep kit        |                           |                      |                         |
| Trizol                                |                           |                      |                         |
| **Antibodies**                        |                           |                      |                         |
| Anti-Zld                              | Harrison et al., 2010     |                      | ChIP: 6 µL , WB: 1:750  |
| Anti-Grh                              | Harrison et al., 2010     |                      | ChIP: 8 µL, WB: 1:1000  |
| Anti-Twi                              | He et al., 2015           |                      | ChIP: 10 µg, WB: 1:1000 |
| Anti-HA-peroxidase clone 3F10         | Roche                     | 12013819001          | WB: 1:500               |
| Anti-Tubulin DM1A                     | Sigma                     | T6199-200UL          | WB: 1:5000              |
| goat anti-rabbit IgG-HRP conjugate    | Bio-Rad                   | 1706515              | WB: 1:3000              |
| Anti-HA clone 12CA5                   | Roche                     |                      | ChIP: 7.5 µL            |
| Anti-H3K27me3                         | Cell Signaling Technology | C36B11; Lot #19      | WB: 1:1000, CR: 0.5 µL  |
|                                       |                           |                      |                         |
|                                       |                           |                      |                         |

@@

@@

**Extended Data Figure 2: Zld and Grh bind to chromatin rapidly after induction of protein expression**

@@

**Extended Data Figure 3: Ectopic expression of pioneer factors in S2 cells leads to widespread changes to chromatin accessibility and gene expression.**

@@

@@

**Extended Data Figure 4: Twist binding leads to chromatin opening and transcriptional activation**

-   Twi volcano and examples

-   TWI RNA-seq volcano and examples

@@

**Extended Data Figure 5: Chromatin features associated with Zld, Grh and Twi binding sites**

@@

**Extended Data Figure 6: Zld, Grh and Twi do not bind preferentially to motifs in a particular position on nucleosomes**

-   De novo motif enrichment for each factor
